A Computational Account of Default-Mode Function\\ by Control Theory and Reinforcement Learning

### 2016-09-22 paper/paper.tex
arranged passages

\title{A Computational Account of Default-Mode Function\\by Control Theory and Reinforcement Learning}

@@

\def\Id{\mathbf{I}}
\def\1{\mathbf{1}}
\def\X{\mathbf{X}}
\def\U{\mathbf{U}}
\def\V{\mathbf{V}}
\def\v{\mathbf{v}}
\def\u{\mathbf{u}}
\def\z{\mathbf{z}}
\def\Y{\mathbf{Y}}
\def\A{\mathbf{A}}
\def\B{\mathbf{B}}
\def\C{\mathbf{C}}
\def\N{\mathbf{N}}
\def\R{\mathbf{R}}
\def\Q{\mathbf{Q}}
\def\P{\mathbf{P}}
\def\W{\mathbf{W}}
\def\K{\mathbf{K}}
\def\a{\mathbf{a}}
\def\b{\mathbf{b}}
\def\s{\mathbf{s}}
\def\x{\mathbf{x}}

@@

\begin{abstract}

the DMN is often proposed to be dedicated to continuous auto- biographical memory retrieval, environmental assessment, emotion ap- praisal, and reward contingency evaluation when letting the mind go.

Constantly tracking and predicting changes in a variable environment is believed to then shape the internal milieu and upcoming external behav- ior adaptively

The model reinterprets many known effects

If this computational models hold some truth in them, the DMNs conceivable key role in the continuous environmental tracking in a generative, integrative process might explain both its highest energy consumption in the brain and its intimate coupling with conscious awareness.

network that might be involved in the automated prediction of social events that modulate behavior

We focus not on normative models (that describe what the brain does), but on process models (that describe how the brain does it)

@@

% official NIPS keywords
\textbf{\\keywords}: Systems Biology, Cognitive Science, Autonomous Learning Systems

@@

@@

\section{The Neurobiological Properties of the Default-Mode Network}
 involvement of the PMC across the boundaries of classical cognitive domains
mPFC and PCC = highest metabolic consumption in the brain/highest level of basal glucose energy consumption in humans

@@

vmPFC regions respond more to the value difference that will be acted on in the current trial (executed in red), and dmPFC to the currently irrelevant value difference (modeled in blue) {Nicolle, 2012 \#3750} individual. Instead activity in vmPFC reflects a choice preference that is executed and rostral dmPFC a choice preference that is modeled. Thus, dorsal regions of rostral mPFC contain value representations in the frame of reference of a modeled (as opposed to an actuated) preference irrespective of whether this applies to another’s or to one’s own likely actions and goals. Likewise, ventral mPFC contains a representation of value in the frame of reference of an executed choice, even if this executed choice reflects one’s own or another’s preferences. dmPFC that reflects the values and preferences of another individual (here temporally discounted at a rate specific to the individual), even when they are not directly relevant to the task at hand. Critically, we also show this activity. While the simplest interpretation of this effect is that the region is simulating one’s own, currently irrelevant, preferences an alternative possibility is that the activity is projec- ting one’s own values into the mind of the partner, while simu- lating the partner’s choices. In essence, estimating the extent to which my own values would influence my partner, if they were making the choice. This iterated reasoning would be.

DMN function has been linked to the recollection of past episodes and the simulation of future episodes

@@

\begin{itemize}
  \item
    vmPFC:
    \begin{itemize}
    \item
the vmPFC sub- serves predominantly non-ambiguous subjective-value-related evaluative processes driven by bottom-up pathways
memory-informed reward and risk estimation of self-relevant environmental stimuli.
\item
the vmPFC might be more closely associated with orches- trating adapted behavior by bottom-up-driven processing of “what matters now”

\item
the vmPFC to monitoring others’ (Lotze et al., 2007) and one’s own (Lane et al., 1997; Phan et al., 2004) emotional responses, that is, other’s (external) emotional reac- tions and one’s own (visceral) arousal. Such real or imagined bodily states, believed to be represented in the vmPFC, proba- bly operate as a bioregulatory disposition governing cognition and decision making (Damasio, 1996; Nauta, 1971), in line with the vmPFC’s functional association with general cognition and reward processing.

@@

\item
In studies of decision making and neuroeconomics, ventromedial prefrontal cortex (vmPFC) con- sistently reflects an individual’s subjective valuation (Behrens et al., 2008; Boorman et al., 2009; Knutson et al., 2005; Plass- mann et al., 2007). By contrast, its dorsomedial neighbor (rostral

@@

@@

\item
processing approach- and avoidance-relevant stimuli

@@

\item
A class of neurons in macaque dorsomedial frontal cortex, including the presupplementary area, responds preferentially to the actions that another macaque makes rather than their own actions (Yoshida et al., 2011)
Many of the same neurons differentiate between another macaque’s actions that were unsuccessful, because the circumstances changed, and actions that were unsuccessful because the other macaque did not make the best choice given the circum- stances. The macaques adjusted their own subsequent actions in different ways after these two types of obser- vations. There is also activity in human dorsomedial prefrontal cortex that reflects expectations about what an observed person will do and errors in such predictions (Suzuki et al., 2012; van Schie et al., 2004)

\item
largely sensory-independent, highly abstract (hence, less tangible) processes across time, space, and content domains.
might be top-down modulated by more dmPFC subserved higher reflective and hypothetical processing.
consistent with present functional decoding, neural activity in the dmPFC, rather than vmPFC, has been con- sistently interpreted to underlie inference, representation, and assessment of one’s own and others’ mental states in functional neuroimaging research

\item
 dmPFC (but not vmPFC) activity was related to the proficiency decline of mental state inference in elderly (Moran et al., 2012), cognitive regulation of one’s own emotional states (Ochsner et al., 2004b) and inference of another person’s emotional states (Ochsner et al., 2004a), as well as self-reported (Wagner et al., 2011) and experimentally measured (Zaki et al., 2009) proficiency in emotional state inference.

@@

\item
 sensory-independent de novo generation of mean- ing representations can only be expected from highly associative, integrative brain areas such as those of the dmPFC subnetwork

\item
the dmPFC subserves a domain-independent neural process

\item
the present results support the dmPFC’s possible involvement in domain-overarching computational mechanisms given its connections to highly associative brain areas and function- ally relation to different complex psychological processes.

\item
the dmPFC was more strongly connected with the inferior frontal gyrus (IFG), temporo-parietal junction (TPJ), and middle temporal gyrus (MTG)

\item
Concluding from previous and present connectivity findings, the dmPFC is preferentially connected with high association and heteromodal cortical areas of the lateral frontal, temporal, and parietal lobe.

\item
it is interesting to note that the vmPFC is more strongly con- nected to medial components of the default mode network (i.e., HC, PCC, RSC), whereas the dmPFC is more strongly con- nected to its lateral components (i.e., IFG, TPJ, and MTG). This dmPFC subnetwork was repeatedly related to self-focused reflec- tion (Andrews-Hanna et al., 2010), contemplation of others’ (Mar, 2011) and one’s own (Lombardo et al., 2009) mental states, mental navigation of the body in space (Maguire et al., 1997), semantic processing (Binder et al., 2009), as well as scene con- struction processes when envisioning past, fictitious, and future events (Hassabis et al., 2007; Spreng et al., 2009; Bzdok et al., 2013).

\item
a VLSM study on disturbed sleep (i.e., a state of mind independent of sensory stimulation but dependent on internally generated informa- tion) exclusively identified the dmPFC (Koenigs et al., 2010).
-> experience replay during sleep

@@

  \item
    PCC (gradients):
    \begin{itemize}
      \item rewards (exploitation) and gathering information about alter- native options (exploration)
Such strategic decisions should incorporate not only recent reward history, but also opportunity costs and environmental statistics

\item
covert reallocation of spatial attention (Gitelman et al., 1999), mediation between internal and external focus (Leech and Sharp, 2014), computation of environmental statistics (Pearson et al., 2009), and self-referential visuospatial imagery (Cavanna and Trimble, 2006)

\item
single-cell recordings in the monkey PCC demonstrated this brain region's sensitivity to subjective target utility (McCoy and Platt, 2005) and integration across individual outcomes in decision making (Pearson et al., 2009).
ng attraction or aversion to options with uncertain or risky rewards
. CGp activation was better predicted by the
subjective salience of a chosen target than by its actual value.

\item
experimental psychologists and behavioral ecologists
have long argued that decision making depends on the conversion
of external variables into a common internal currency of value.

\item
electrophys- iological research in animals implicated the PCC in strategic selection (Pearson et al., 2009), risk assessment (McCoy and Platt, 2005), and outcome-contingent behavioral modulation (Hayden et al., 2008), while the RSC was implicated in nav- igation and approach-avoidance behavior (Vann et al., 2009).

\item
(McCoy and Platt, 2005):
t internal representations of value lie at the very core of
decision making,
visual gambling task used in the current study affords a unique
opportunity to examine neural activity under conditions in which
subjective value, but not objective value, varied, as indicated by
subjects’ choices
-> value matrix is not the same in each agent
h the direction of impending
Our data extend those
findings, demonstrating a direct relationship between subjective preferences
for uncertain rewards, or the opportunity to harvest a
relatively large reward, and the activity of neurons thought to participate
in the allocation of attention
movement, as shown previously24,30, and the uncertainty of rewards
associated with this movement
CGp appears to carry spatial information that is scaled by
subjective preferences for particular patterns of reward outcome.
Our data indicate that CGp
neurons signal subjective biases for uncertain rewards (or, perhaps, the
potential to receive a large reward) rather than objective target value.
the spatial sensitivity of CGp neurons was enhanced under
conditions of high risk.
-> delay discounting / non-immediate reward -> reinforcement learning

\item
Pearson2009:
balance. Here we show that CGp neurons distinguish be- tween exploratory and exploitative decisions made by mon- keys in a dynamic foraging task.
 option switching [11] and integrate this information across multiple trials [11], but the present

 \item
 Together, these results invite the hypothesis that CGp is part of a network that monitors the outcomes of individual deci- sions and integrates that information into higher-level strate- gies spanning multiple choices

@@

\item
choosing among multiple tar-
gets whose relative values changed dynamically,
neurons in posterior cingulate cortex signaled the distinction between trials on which monkeys pursued an exploratory rather than an exploitative strategy.
**learn its current value and integrate this information with their statistical knowledge of the environment to predict its relative value on upcoming trials.**

\item
Hayden2008: adapativity of subjective reward schedules tht impact the action choices
 lesion (Gabriel, 1990) studies strongly implicate CGp in working mem- ory, attention, and general arousal (Raichle and Mintun, 2006)— all processes that contribute to adaptive decision making. -> gradient defect

\item
corded activity of single neurons in monkeys per- forming a gambling task in which the reward outcome of each choice strongly influenced subsequent choices.
choices. We found that CGp neurons signaled reward outcomes in a nonlinear fashion and that outcome- contingent modulations in firing rate persisted into subsequent trials. Moreover, firing rate on any one trial predicted switching to the alternative option on the next trial. Finally, microstimulation in CGp follow- ing risky choices promoted a preference reversal for the safe option on the following trial. Collectively, these results demonstrate that CGp directly contrib- utes to the evaluative processes that support dynamic changes in decision making in volatile environments.

\item
 these observations suggest the hypothesis that CGp contributes to the integration of actions and their out- comes and thereby influences subsequent changes in behavior.
 We confirmed a causal role for CGp in outcome evaluation and behavioral adjustment by showing that microstimulation following the most desired reward out- come increased the likelihood of exploring the alternative on the next trial.

 \item
signal decision outcomes in a nonlinear fashion, maintain this information in a buffer between trials, and predict future changes in behavior. Moreover, microstimulation in CGp promotes explo- ration of the previously antipreferred option.

\item
highlight the dynamic nature of information processing in CGp, which is not restricted to any single epoch or aspect of task performance but instead continuously adapts to changes in both the external environment and internal milieu.

\item
(Patho-)Physiologically, meta- bolic fluctuations in the human PMC have been closely related to vari- ous instances of altered conscious awareness, including anesthesia (Fiset et al., 1999), sleep (Maquet, 2000), and restoration from vegeta- tive states (Laureys et al., 1999).

  \item
Electrophysiologically, gamma band re- cordings in humans (Dastjerdi et al., 2011) and single-cell recordings in monkeys (Hayden et al., 2009) revealed activity reductions in the PMC during attentionally demanding tasks compared to rest.

\item
 have long been speculated to reflect constant contemplation of (external) environment and (internal) memory

 \item
   xons in parts of the PMC myelinate comparatively late during postnatal development in monkeys (Goldman- Rakic, 1987). Such late postnatal myelination is generally believed to occur in the phylogenetically most developed associations regions (Flechsig, 1920), t

\item
only cluster 2 was congruently coupled (across MACM and RSFC) with the amygdala (involved in significance evaluation) and the nucleus accumbens (involved in reward evaluation)
s well as exclusively functionally asso- ciated with facial appraisal. Similarly, the human vPCC was the only PMC region connected to the laterobasal (rather than centromedial or superficial) nuclei group of the amygdala (Bzdok et al., 2013b), which is an amygdalar subregion probably devoted to continuously scanning environmental input for biological significance (Adolphs, 2010; Aggleton et al., 1980; Bzdok et al., 2011; Ghods-Sharifi et al., 2009; LeDoux, 2007).

\item Bálint's syndrome: neurological disorder of conscious
awareness resulting from damage in bilateral parietal cortex;
"psychic paralysis of gaze", that is, the inability for internally
motivated, targeted saccades hindering fixation of currently not
attended features in the field of view (i.e., oculomotor apraxia).
unable to bind various individual features of the visual
environment into an integrated whole (i.e., simultanagnosia)
as well as unable to navigate hand movement to a targeted
object helped by vision (i.e., optic ataxia).
difficulty avoiding running into objects placed ahead;
challenged in estimating distances as well as perceiving
spatial depth, object sizes and object orientation

  \item
    vPCC:
the ventral visual stream—the “what” system for object process- ing (Ungerleider and Haxby, 1994; Ungerleider and Mishkin, 1982; Vogt et al., 2006), contrary to the dPCC's conceivable relation to the dorsal “where” system
\item
  dPCC:
This view is in line with the well-known integration of the dPCC in the dorsal visual stream—the “where” system for spatial processing (Ungerleider and Haxby, 1994; Ungerleider and Mishkin, 1982; Vogt et al., 2006), in contrast to vPCC's relation to the ventral “what” system
\end{itemize}

  \item
    RTPJ:
    \begin{itemize}
\item
Corbetta2008:
Although both attentional networks have been most exten- sively investigated in vision, the available evidence indicates a supramodal function (Driver and Spence, 1998; Macaluso et al., 2002). The ventral network (right TPJ, right IFG) registers salient events in the environment not only in the visual but also in the auditory and tactile modalities (Downar et al., 2000)
Several lines of evidence indicate that two cortico-cortical neural systems are involved in attending to environmental stimuli (Corbetta and Shulman, 2002). A dorsal frontoparietal network. A second system, the ventral frontoparietal network, is not ac- tivated by expectations or task preparation but responds along with the dorsal network when behaviorally relevant objects (or targets) are detected (Corbetta et al., 2000). Both dorsal and ventral networks are also activated during reorienting, with en- hanced responses during the detection of targets that appear at unattended locations. For example, enhanced responses are observed when subjects are cued to expect a target at one location but it unexpectedly appears at another (i.e., ‘‘invalid’’ targets in the Posner spatial cueing paradigm)
or when a target appears infre- quently, as in ‘‘oddball’’ paradigms.

\item
blanke:
the core region of the human vestibular cortex is situated close to the angular gyrus10. It is possible that the experience of dissociation of self from the body is a result of failure to integrate complex somatosensory and vestibular information.
Initial stimulations (n 3; 2.0–3.0 mA) induced vestibular responses, in which the patient reported that she was “sinking into the bed” or “falling from a height”.

\item
high-level social cognition also engenerded expectation violations
-> that's why coincides with "agency" meta-analytic location
(Decety 2007):
suggest that activation in the TPJ during social cognition may therefore rely on a lower-level computational mech- anism involved in generating, testing, and correcting internal predictions about external sensory events.

\item
Sridharan: RTPJ involved in bottom-up saliency detection

pRTPJ cluster was also functionally associated with deception tasks

\item
  LTPJ
  \begin{itemize}
\item
the difference between the two task groups could be parsimoniously explained by the required atten- tion to either the external world or self.
world -> policy matrix driven computation
self -> value matrix driven computation

\item
only the left TPJ was associated with language processes, whereas only the right TPJ was functionally associated with attention processes

\item 
Wernicke's area:
involved in accessing and integrating world knowlege.
involved in the comprehension or understanding of written and spoken language Damage caused to Wernicke's area results in receptive, fluent aphasia. This means that the person with aphasia will be able to fluently connect words, but the phrases will lack meaning.
A major impairment of language comprehension, while speech retains a natural-sounding rhythm and a relatively normal syntax. Language as a result is largely meaningless. difficulty finding words, putting words in the wrong order, substituting sounds and/or words, difficulty understanding spoken utterances, difficulty recognizing some words by sight, difficulty writting letters

\item HC:
\begin{itemize}
  \item
The HC, in turn, is well known to be involved in memory and spatial navigation in animals and humans (von Bechterew, 1900; Scoville and Milner, 1957; O’Keefe and Dostrovsky, 1971; Maguire et al., 2000).

@@

\item
They found that amnesic patients with bilateral hippocampal damage were markedly impaired relative to matched control subjects at imagining new fictitious experiences (Figure 1). Moreover, Hassabis et al. [21] identified a possible source for this deficit. Although patients were able to produce considerable detail when asked to imagine fictitious new experiences, their descriptions lacked spatial coherence and were instead fragmented and considerably less rich [21].

\item
 empirical evidence hinting at a two-process function of the hippocampus comes from structural MRI studies of expert navigators (London taxi drivers) who show increased grey matter volume in posterior hippocampus seemingly at the expense of reduced grey matter volume in anterior hippocampus (Maguire et al. 2006b). Moreover, their increased spatial knowledge appears to come at a cost to the acquisition of new visual associative information (Maguire et al. 2006b; Woollett \& Maguire 2009).

\item
Schachter/Buckner:
The network described here is tied to the medial temporal lobe system, which is traditionally considered almost exclusively in the context of remembering the past. We suspect the adaptive value of
episodic memory is not solely in its ability to afford mental reconstruction of the past but rather in its contribution to building mental models – simulations – of what might happen next or other perspectives on the immediate envir- onment, such as what others are thinking (see Ref. [63]). As

\item
the GMV of the entorhinal cortex (connectionally and functionally closely coupled with the HC) correlated with social network size (Kanai et al., 2012)

\item 
In fact, phase-locked hippocampal?<80><93>cortical loops have been proposed t
formation of mnemonic neuronal representations
**a large body of animal and human literature relates
hippocampal-prefrontal theta to memory and memory to the DMN**

@@

@@

\item
sequential single- cell recording could reveal such cooperative patterns

\item
buszaki2004 theta oscillations:
Using large-scale recordings, researchers can follow complex patterns for extended time periods and determine whether their modification by experience will influence self-generated patterns in the absence of envi- ronmental inputs. Spike sequences, imposed upon the network by behavioral manipulations, recur spontaneously during subsequent sleep
indicating that neurons organize themselves into preferred cell assemblies, and the seeds of emergence stem from experi- ence-related activity.
 Such internally driven, self-organized assemblies may reflect mechanisms that give rise to cognitive phenomena
 Sharp-wave ripples are believed to be the transfer mechanism of information from the hippocampus to neocortex during off-line (eg, sleep) states.
Neurons, mostly studied in the hippocampus, which fire action potentials only when the animal is in a specific place in a given environment (that place where a cell fires is called the “place field” of that cell).
-> self-play in deepmind Go

\item
statistical structure of hippocampal activity ->
spatial maps of surroundings are encoded

\item
Numerous experiments have demonstrated that hippocampal neurons show place-related firing while the rat explores or traverses its environment so that each assembly of hippocampal principal cells defines a particular position of space

@@

\item
coding, transfer, and consolidation of
information
This emerging picture of hippocampal dy- namics suggests that neurons at the opposite ends of the distributions may convey differ- ent but complementary types of information. The ever-active minority of place cells may be responsible for generalizing across envi- ronments and affords the brain the capacity to regard no situation as completely un- known because every alley, mountain, river, or room has elements of previously experi- enced similar situations. In many situations,
this minority provides the “best guess” of the hippocampus and offers “good enough” solutions to get by. On the other hand, the majority of less active neurons constitute a large reservoir that can be mobilized (7) to precisely distinguish one situation from an- other and incorporate novel ones as distinct.

@@

  \end{itemize}
\end{itemize}

@@

\section{Relation to Other Statistical Models (Elvis)}
\paragraph{Control Theory.}
\begin{itemize}
  \item The model proposed in \cite{betzel2016} can be cast in the form \eqref{eq:hj}, with the particular choice $\Q = \textbf{I} = \rho^{-1}\R$ and $\Q_{\text{fin}} = \textbf{0}$, but with a rather ad-hoc handle on stability issues and choice driver nodes...
\end{itemize}

>>>>

\title{A Computational Account of Default-Mode Function\\
by Control Theory and Reinforcement Learning}

@@

\def\Id{\mathbf{I}}
\def\1{\mathbf{1}}
\def\X{\mathbf{X}}
\def\U{\mathbf{U}}
\def\V{\mathbf{V}}
\def\v{\mathbf{v}}
\def\u{\mathbf{u}}
\def\z{\mathbf{z}}
\def\Y{\mathbf{Y}}
\def\A{\mathbf{A}}
\def\B{\mathbf{B}}
\def\C{\mathbf{C}}
\def\N{\mathbf{N}}
\def\R{\mathbf{R}}
\def\Q{\mathbf{Q}}
\def\P{\mathbf{P}}
\def\K{\mathbf{K}}
\def\a{\mathbf{a}}
\def\b{\mathbf{b}}
\def\s{\mathbf{s}}
\def\x{\mathbf{x}}

@@

\begin{abstract}
The default mode network (DMN) is the neural representation of the human
baseline mental activity.
%
Many research streams agree on its likely role in evolutionarily adaptive envisioning of past and hypothetical scenarios to predict the environment.
The DMN would hence be dedicated to continuous autobiographical memory retrieval, generate hypothetical outcomes,
and reward contingency evaluation when letting the mind go.
It explains its highest energy consumption in the brain and its intimate coupling with conscious awareness.
%
This concept paper proposes a process model that describes
\textit{how} the DMN may actually implement continuous
environmental assessment and prediction.
DMN function is recast from the mathematical perspective of control theory and
reinforcement learning.
Neurobiological evidence on the human and animal DMN
is linked to recent progress in autonomous systems research
in the machine-learning domain.
We argue that this engineering account can parsimoneously
explain a variety of existing neuroscientific hypotheses of DMN function.
%
Formal models of the computational processes subserved by the DMN
could offer statistical control of predictive human behavior.

@@

% official NIPS keywords
\textbf{\\keywords}: Systems Biology, mind wandering, cognitive science,
autonomous learning systems
\textbf{\\Get opinion from}: Danielle Bassett, Kai Vogeley, Mohammad Shakir

@@

Its societal and economic relevance is certified by involvement in various psychiatric disorders, including schizophrenia, autism, and depression.

@@

\section{The Neurobiological Properties of the Default-Mode Network}
mPFC and PCC = highest metabolic consumption in the brain/highest level of basal glucose energy consumption in humans

involvement of the PMC across the boundaries of classical cognitive domains

@@

vmPFC regions respond more to the value difference that will be acted on in the current trial (executed in red), and dmPFC to the currently irrelevant value difference (modeled in blue) {Nicolle, 2012 \#3750} individual. Instead activity in vmPFC reflects a choice preference that is executed and rostral dmPFC a choice preference that is modeled. Thus, dorsal regions of rostral mPFC contain value representations in the frame of reference of a modeled (as opposed to an actuated) preference irrespective of whether this applies to another’s or to one’s own likely actions and goals. Likewise, ventral mPFC contains a representation of value in the frame of reference of an executed choice, even if this executed choice reflects one’s own or another’s preferences. dmPFC that reflects the values and preferences of another individual (here temporally discounted at a rate specific to the individual), even when they are not directly relevant to the task at hand.

@@

\begin{itemize}
  \item
    vmPFC:
    \begin{itemize}
    \item
the vmPFC sub- serves predominantly non-ambiguous subjective-value-related evaluative processes
reward-informed and risk estimation of self-relevant environmental stimuli.
\item
the vmPFC might be more closely associated with orches- trating adapted behavior by bottom-up-driven processing of “what matters now”

\item
the vmPFC to monitoring others’ (Lotze et al., 2007) and one’s own (Lane et al., 1997; Phan et al., 2004) emotional responses, that is, other’s (external) emotional reac- tions and one’s own (visceral) arousal. Such real or imagined bodily states, believed to be represented in the vmPFC, proba- bly operate as a bioregulatory disposition governing cognition and decision making (Damasio, 1996; Nauta, 1971)

@@

\item
In studies of decision making and neuroeconomics, ventromedial prefrontal cortex (vmPFC) con- sistently reflects an individual’s subjective valuation (Behrens et al., 2008; Boorman et al., 2009; Knutson et al., 2005; Plass- mann et al., 2007)

@@

\item
Schuck 2016: Performance within and across participants was related to state encoding in OFC;
“cognitive map” of task space in which the current state of the task is represented, and this representation is especially critical for behavior when states are unobservable from sensory input

@@

@@

\item
sensory-independent de novo generation of meaning representations

\item
underlie inference, representation, and assessment
such as in one’s own and others’ mental states in functional neuroimaging research

\item
There is also activity in human dorsomedial prefrontal cortex that reflects expectations about what an observed person will do and errors in such predictions (Suzuki et al., 2012; van Schie et al., 2004)
largely sensory-independent, highly abstract (hence, less tangible) processes across time, space, and content domains.
hypothetical processing.

\item
A class of neurons in macaque dorsomedial frontal cortex, including the presupplementary area, responds preferentially to the actions that another macaque makes rather than their own actions (Yoshida et al., 2011)
Many of the same neurons differentiate between another macaque’s actions that were unsuccessful, because the circumstances changed, and actions that were unsuccessful because the other macaque did not make the best choice given the circum- stances. The macaques adjusted their own subsequent actions in different ways after these two types of obser- vations.

\item
 dmPFC (but not vmPFC) activity was related to the proficiency decline of mental state inference in elderly (Moran et al., 2012)

@@

scene con- struction processes when envisioning past, fictitious, and future events (Hassabis et al., 2007; Spreng et al., 2009; Bzdok et al., 2013).

@@

  \item
    PMC (gradients):
    \begin{itemize}
      \item
      PMC myelinate comparatively late during postnatal development in monkeys (Goldman- Rakic, 1987). generally a sign of phylogenetic sophistication (Flechsig, 1920)
      \item
      (Patho-)Physiologically, meta- bolic fluctuations in the human PMC have been closely related to vari- ous instances of altered conscious awareness, including anesthesia (Fiset et al., 1999), sleep (Maquet, 2000), and restoration from vegeta- tive states (Laureys et al., 1999).      
      \item
      electrophys- iological research in animals implicated the PCC in strategic selection (Pearson et al., 2009), risk assessment (McCoy and Platt, 2005), and outcome-contingent behavioral modulation (Hayden et al., 2008), while the RSC was implicated in nav- igation and approach-avoidance behavior (Vann et al., 2009).

      \item
      Electrophysiologically, gamma band re- cordings in humans (Dastjerdi et al., 2011) and single-cell recordings in monkeys (Hayden et al., 2009) revealed
      \textit{activity reductions} in the PMC
      during task performance compared to rest.

      \item
      have long been speculated to reflect constant contemplation of (external) environment and (internal) memory, as an "inner minds eye"

      \item Bálint's syndrome: neurological disorder of conscious
      awareness resulting from damage in bilateral parietal cortex.
      inability to bind various individual features of the visual
      environment into an integrated whole (i.e., simultanagnosia)
      as well as to direct action towards 
      current unattended environmental objects
      (i.e., optic ataxia).

      This can viewed as an impairment in the gathering
      of information about alternative options (i.e., exploration) as well as
      leveraging these environmental opportunities
      (i.e., exploitation).

      \item
      neurons in posterior cingulate cortex signaled the distinction between trials on which monkeys pursued an exploratory rather than an exploitative strategy.

      \item
      Pearson2009:
      balance. Here we show that CGp neurons distinguish be- tween exploratory and exploitative decisions made by mon- keys in a dynamic foraging task.

      \item
      computation of environmental statistics (Pearson et al., 2009):

      single-cell recordings in the monkey PCC demonstrated this brain region's sensitivity to subjective target utility (McCoy and Platt, 2005) and integration across individual outcomes in decision making (Pearson et al., 2009).
      ng attraction or aversion to options with uncertain or risky rewards
      . CGp activation was better predicted by the
      subjective salience of a chosen target than by its actual value.

      -> internal currency of value

      motivated, targeted saccades hindering fixation of currently not
      attended features in the field of view (i.e., oculomotor apraxia).

      \item
      only cluster 2 was congruently coupled (across MACM and RSFC) with the amygdala (involved in significance evaluation) and the nucleus accumbens (involved in reward evaluation)
      s well as exclusively functionally asso- ciated with facial appraisal. Similarly, the human vPCC was the only PMC region connected to the laterobasal (rather than centromedial or superficial) nuclei group of the amygdala (Bzdok et al., 2013b), which is an amygdalar subregion probably devoted to continuously scanning environmental input for biological significance (Adolphs, 2010; Aggleton et al., 1980; Bzdok et al., 2011; Ghods-Sharifi et al., 2009; LeDoux, 2007).
      \item
      (McCoy and Platt, 2005):
      internal representations of subjective value lie at the very core of
      decision making,
      task where subjective value, but not objective value, varied, as indicated by
      subjects’ choices
      -> value matrix is not the same in each agent
      h the direction of impending
      Our data extend those
      findings, demonstrating a direct relationship between subjective preferences
      for uncertain rewards, or the opportunity to harvest a
      relatively large reward, and the activity of neurons thought to participate
      in the allocation of attention
      movement, as shown previously24,30, and the uncertainty of rewards
      associated with this movement
      CGp appears to carry spatial information that is scaled by
      subjective preferences for particular patterns of reward outcome.
      Our data indicate that CGp
      neurons signal subjective biases for uncertain rewards (or, perhaps, the
      potential to receive a large reward) rather than objective target value.
      the spatial sensitivity of CGp neurons was enhanced under
      conditions of high risk.
      -> delay discounting / non-immediate reward -> reinforcement learning

Such strategic decisions should incorporate not only recent reward history, but also opportunity costs and environmental statistics

\item
microstimulation in CGp promotes explo- ration of the previously antipreferred option.

@@

\item
outcome- contingent modulations in firing rate persisted into subsequent trials. Moreover, firing rate on any one trial predicted switching to the alternative option on the next trial. Finally, microstimulation in CGp follow- ing risky choices promoted a preference reversal for the safe option on the following trial. Collectively, these results demonstrate that CGp directly contrib- utes to the evaluative processes that support dynamic changes in decision making in volatile environments.

\item
IN SUM, these results suggest that the PCC is part of a network that monitors the subjective outcomes of possible decisions and integrates that information into higher-level strategies
**learn its current value and integrate this information with their statistical knowledge of the environment to predict its relative value on upcoming trials.**
\item
information processing in the CGp continuously adapts to changes in both the external environment and internal milieu.
\item
Hayden2008: adapativity of subjective reward schedules tht impact the action choices
lesion (Gabriel, 1990) studies strongly implicate CGp in working mem- ory, attention, and general arousal (Raichle and Mintun, 2006)— all processes that contribute to adaptive decision making. -> gradient defect
\item
integration of actions and their out- comes and thereby influences subsequent changes in behavior.
We confirmed a causal role for CGp in outcome evaluation and behavioral adjustment

\item HC:
\begin{itemize}
  \item
  Schachter/Buckner:
  The network described here is tied to the medial temporal lobe system, which is traditionally considered almost exclusively in the context of remembering the past. We suspect the adaptive value of
  episodic memory is not solely in its ability to afford mental reconstruction of the past but rather in its contribution to building mental models – simulations – of what might happen next or other perspectives on the immediate envir- onment, such as what others are thinking

  \item
The HC, in turn, is well known to be involved in memory and spatial navigation in animals and humans (von Bechterew, 1900; Scoville and Milner, 1957; O’Keefe and Dostrovsky, 1971; Maguire et al., 2000).

@@

\item
bilateral hippocampal damage were markedly impaired relative to matched control subjects at imagining new fictitious experiences (Hassabis), their descriptions lacked spatial coherence and were instead fragmented and considerably less rich

@@

\item
 structural MRI studies of expert navigators (London taxi drivers) who show increased grey matter volume in posterior hippocampus seemingly at the expense of reduced grey matter volume in anterior hippocampus (Maguire et al. 2006b)

@@

\item
statistical structure of hippocampal activity ->
spatial maps of surroundings are encoded
buszaki2004 theta oscillations:
Using large-scale recordings, researchers can follow complex patterns for extended time periods and determine whether their modification by experience will influence self-generated patterns in the absence of envi- ronmental inputs. Spike sequences, imposed upon the network by behavioral manipulations, recur spontaneously during subsequent sleep
indicating that neurons organize themselves into preferred cell assemblies, and the seeds of emergence stem from experi- ence-related activity.

Neurons, mostly studied in the hippocampus, which fire action potentials only when the animal is in a specific place in a given environment (that place where a cell fires is called the “place field” of that cell).

Numerous experiments have demonstrated that hippocampal neurons show place-related firing while the rat explores or traverses its environment so that each assembly of hippocampal principal cells defines a particular position of space

@@

-> self-play in deepmind Go

\item
coding, transfer, and consolidation of information:
This emerging picture of hippocampal dy- namics suggests that neurons at the opposite ends of the distributions may convey differ- ent but complementary types of information. The ever-active minority of place cells may be responsible for generalizing across envi- ronments and affords the brain the capacity to regard no situation as completely un- known because every alley, mountain, river, or room has elements of previously experi- enced similar situations. In many situations,
this minority provides the “best guess” of the hippocampus and offers “good enough” solutions to get by. On the other hand, the majority of less active neurons constitute a large reservoir that can be mobilized (7) to precisely distinguish one situation from an- other and incorporate novel ones as distinct.

@@

  \item
    RTPJ:
    \begin{itemize}
\item
Sridharan: RTPJ involved in bottom-up saliency detection

\item
Corbetta2008:
Although both attentional networks have been most exten- sively investigated in vision, the available evidence indicates a supramodal function (Driver and Spence, 1998; Macaluso et al., 2002). The ventral network (right TPJ, right IFG) registers salient events in the environment not only in the visual but also in the auditory and tactile modalities (Downar et al., 2000)
Several lines of evidence indicate that two cortico-cortical neural systems are involved in attending to environmental stimuli (Corbetta and Shulman, 2002). A dorsal frontoparietal network. A second system, the ventral frontoparietal network, is not ac- tivated by expectations or task preparation but responds along with the dorsal network when behaviorally relevant objects (or targets) are detected (Corbetta et al., 2000). Both dorsal and ventral networks are also activated during reorienting, with en- hanced responses during the detection of targets that appear at unattended locations. For example, enhanced responses are observed when subjects are cued to expect a target at one location but it unexpectedly appears at another (i.e., ‘‘invalid’’ targets in the Posner spatial cueing paradigm)
or when a target appears infre- quently, as in ‘‘oddball’’ paradigms.

\item
  LTPJ
  \begin{itemize}
    \item 
    Wernicke's area:
    involved in accessing and integrating world knowlege.
    involved in the comprehension or understanding of written and spoken language Damage caused to Wernicke's area results in receptive, fluent aphasia. This means that the person with aphasia will be able to fluently connect words, but the phrases will lack meaning.
    A major impairment of language comprehension, while speech retains a natural-sounding rhythm and a relatively normal syntax. Language as a result is largely meaningless. difficulty finding words, putting words in the wrong order, substituting sounds and/or words, difficulty understanding spoken utterances, difficulty recognizing some words by sight, difficulty writting letters

\item
the difference between the two task groups could be parsimoniously explained by the required atten- tion to either the external world or self.
world -> policy matrix driven computation
self -> value matrix driven computation

@@

\section{Relation to Other Statistical Models (Elvis)}
\paragraph{Control Theory.}
abc
